Is it Better to be a Moose or a Black Bear?

### 2024-04-23 outputs/paper/paper.qmd
Finished datasheet and saved data as parquet files

#### Read in data ####
north_bear <-
  read_parquet(
    file = "../data/analysis_data/north_data_bear.parquet"
  )

se_bear <-
  read_parquet(
    file = "../data/analysis_data/southeast_data_bear.parquet"
  )

sw_bear <-
  read_parquet(
    file = "../data/analysis_data/southwest_data_bear.parquet"
  )

north_moose <-
  read_parquet(
    file = "../data/analysis_data/north_data_moose.parquet"
  )

se_moose <-
  read_parquet(
    file = "../data/analysis_data/southeast_data_moose.parquet"
  )

sw_moose <-
  read_parquet(
    file = "../data/analysis_data/southwest_data_moose.parquet"
  )

all_moose <-
  read_parquet(
    file = "../data/analysis_data/all_data_moose.parquet"
  )

types_moose <-
  read_parquet(
    file = "../data/analysis_data/types_data_moose.parquet"
  )

all_bear <-
  read_parquet(
    file = "../data/analysis_data/all_data_bear.parquet"
  )
```

>>>>

#### Read in data ####
north_bear <-
  read_parquet(
    file = "../analysis_data/north_data_bear.parquet"
  )

se_bear <-
  read_parquet(
    file = "../analysis_data/southeast_data_bear.parquet"
  )

sw_bear <-
  read_parquet(
    file = "../analysis_data/southwest_data_bear.parquet"
  )

north_moose <-
  read_parquet(
    file = "../analysis_data/north_data_moose.parquet"
  )

se_moose <-
  read_parquet(
    file = "../analysis_data/southeast_data_moose.parquet"
  )

sw_moose <-
  read_parquet(
    file = "../analysis_data/southwest_data_moose.parquet"
  )

all_moose <-
  read_parquet(
    file = "../analysis_data/all_data_moose.parquet"
  )

types_moose <-
  read_parquet(
    file = "../analysis_data/types_data_moose.parquet"
  )

all_bear <-
  read_parquet(
    file = "../analysis_data/all_data_bear.parquet"
  )
```
